### 2020-11-10 doc/manuscript/Dow_manuscript.Rmd
incorporating refs
#19

Leaf phenology--as characterized by satellite observations of NDVI or EVI-- is linked to the ecosystem CO~2~ uptake period. In turn, longer carbon uptake periods have been linked to greater net annual C sequestration (i.e., net ecosystem exchange, NEE) by ecosystems [@churkina_spatial_2005; @keenan_net_2014], although more of the interannual variation in forest NEE is explained by variation in maximum C uptake rates than by the length of the carbon uptake period [@fu_maximum_2019].

Many observations of climate induced phenological shifts are based on GIS (), eddy-covarience measurements (), or other broad scale measurements of phenological timing, and do little to discern differences between individual species, where leaf and stem-growth phenology can be decoupled (D'Orangeville et al, in review).

>>>>

Leaf phenology is linked to the ecosystem CO~2~ uptake period, and in turn longer carbon uptake periods have been linked to greater net annual C sequestration (*i.e.*, net ecosystem exchange, $NEE$; @churkina_spatial_2005; @keenan_net_2014; @zhou_explaining_2016]. 
However, more of the interannual variation in forest $NEE$ is explained by variation in maximum C uptake rates than by the length of the carbon uptake period [@zhou_explaining_2016; @fu_maximum_2019].

Thus, while it is increasingly clear that warming spring temperatures lengthen the growing season and modestly increase annual carbon sequestration, we know little about the effect on tree growth and woody productivity, which can be decoupled from leaf phenology and represent only a modest proportion of $NEE$.

~~,Many observations of climate induced phenological shifts are based on GIS (), eddy-covarience measurements (), or other broad scale measurements of phenological timing, and do little to discern differences between individual species, where leaf and stem-growth phenology can be decoupled (D'Orangeville et al, in review). ~~
